Distance Sampling in \proglang{R}

### 2016-03-31 paper.tex
fix shortnames for bibliography

\documentclass[article]{jss}
\usepackage[utf8]{inputenc}

@@

The Windows program Distance (or ``DISTANCE''; for clarity henceforth
``Distance for Windows'') can be used to fit detection functions to
distance sampling data. It was first released (versions 1.0 - 3.0;
principally programmed by Jeff Laake while working at the National
Marine Mammal Laboratory) as a console-based application (this in turn
was based on earlier software TRANSECT, \citet{Burnham:1980wz} and
algorithms developed in \citet{Buckland:1992fa}), before the first
graphical interface (Distance for Windows 3.5) was released in November
1998. Since this time it has evolved to include various design and
analysis features \citep{Thomas:2010cf}. Distance for Windows versions 5
onwards have included \proglang{R} \citep{rcore} packages as the
analysis engines providing additional, more complex analysis options
than those offered by the original (FORTRAN) code.

>>>>

\documentclass[article,shortnames]{jss}
\usepackage[utf8]{inputenc}

@@

The Windows program Distance (or ``DISTANCE''; for clarity henceforth
``Distance for Windows'') can be used to fit detection functions to
distance sampling data. It was first released (versions 1.0 - 3.0;
principally programmed by Jeff Laake while working at the National
Marine Mammal Laboratory) as a console-based application (this in turn
was based on earlier software TRANSECT, \citet{Burnham:1980wz} and
algorithms developed in \citet{Buckland:1992fa}), before the first
graphical interface (Distance for Windows 3.5) was released in November
1998. Since this time it has evolved to include various design and
analysis features \citep{Thomas:2010cf}. Distance for Windows versions 5
onwards have included \proglang{R} \citep{rcore} packages as the
analysis engines providing additional, more complex analysis options
than those offered by the original (Fortran) code.
